### 2014-04-09 docs/results/results.tex
first commit

\documentclass[letterpaper]{article}
\setlength{\columnsep}{0.75cm}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}
\usepackage[hmargin=1in,vmargin=1in]{geometry}
\setlength{\parindent}{0cm}
\setlength{\parskip}{4mm plus1mm minus1mm}
\usepackage[
	colorlinks=true,
	urlcolor=blue
]{hyperref}

@@

\parindent0pt \parskip8pt
\begin{document}
\maketitle
\section{Classifier competence as a function of image}
\includegraphics[scale=0.75]{../figs/longitude0.pdf}

The following figure investigates the ability of a naive bayes classifier to 
classify workers who were primed under different treatments.  Specifically, 
we consider the binary classification task of classifying workers who drawn 
from either the cultural-images or ingredients-images treatments.

@@

>>>>

\documentclass[letterpaper]{article}
\setlength{\columnsep}{0.75cm}
\usepackage{python}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}
\usepackage[hmargin=1in,vmargin=1in]{geometry}
\setlength{\parindent}{0cm}
\setlength{\parskip}{4mm plus1mm minus1mm}
\usepackage[
	colorlinks=true,
	urlcolor=blue
]{hyperref}

@@

\parindent0pt \parskip8pt
\begin{document}
\maketitle
\section{Classifier competence as a function of image}

\begin{center}
\includegraphics[scale=0.65]{../figs/longitude_cult-ing-img.pdf}
\end{center}

The above figure investigates the ability of a naive bayes classifier to 
classify workers who were primed under different treatments.   
We perform binary classification of workers drawn 
from either the cultural-images or ingredients-images treatments.

@@

\begin{center}
\includegraphics[scale=0.65]{../figs/longitude_cult-ing-fund.pdf}
\end{center}
This figure is similar to the previous one, but it compares the cultural-funder
and ingredients-funder treatments.

\begin{center}
\includegraphics[scale=0.65]{../figs/longitude_cult-ing-img-fund.pdf}
\end{center}
And this one compares the cultural-funder-image and ingredients-funder-image
treatments

\begin{center}
\includegraphics[scale=0.65]{../figs/cross-classification.pdf}
\end{center}
The above figure shows that, from the perspective of being able to distinguish
priming treatments using a naive bayes classifier, in-task priming is has as
great an effect as prominent disclusure of the research funder.

\begin{center}
\includegraphics[scale=0.65]{../figs/valenceComparison.pdf}
\end{center}
The above figure shows the effect of the various priming treatments in terms
of the number of culture-related and food-related words used.
